Analyzing X-ray images in Python with scikit-image

### 2016-08-21 skimage_tomo.tex
Added mayavi example

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.8\textwidth]{jupyter_example}}
    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
             plot and text output (middle), and free-form narrative text (bottom).
             This makes it ideal to record and report code-based analyses.
             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
 \label{fig:jupyter}}
\end{figure*}

@@

Visualizing images is an important component of the image processing
workflow, used to inspect the final result and to adjust the
parameters of intermediate processing operations.
\texttt{matplotlib} \citep{Hunter2007} is the most popular 2D plotting
library of the Python ecosystem. It can be used to visualize 2D data such
as color or grayscale images, and 1D data such as contour lines, outlines
of segmented regions, histograms of gray levels, etc. Although
\texttt{matplotlib} has simple 3D plotting capabilities, we
recommend using the \texttt{mayavi} module \citep{Ramachandran2011}
for applications requiring advanced 3D visualization, such as tomography. 
\texttt{mayavi} is based on the VTK toolkit. It exposes a simple API for
visualizing data passed as \texttt{numpy} arrays. For more advanced
visualizations, a large majority of VTK capabilities can be accessed
through mayavi's pipeline API.
\texttt{mayavi} offers a good trade-off between simplicity of use for
common operations, and accessibility to more sophisticated
capabilities such as responsive
visualizations.

>>>>

\begin{figure*}[ht!]
    \centerline{\includegraphics[width=0.8\textwidth]{jupyter_example}}
    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
             plot and text output (middle), and free-form narrative text (bottom).
             This makes it ideal to record and report code-based analyses.
             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
 \label{fig:jupyter}}
\end{figure*}

@@

@@

Visualizing images is an important component of the image processing
workflow, used to inspect the final result and to adjust the
parameters of intermediate processing operations.
\texttt{matplotlib} \citep{Hunter2007} is the most popular 2D plotting
library of the Python ecosystem. It can be used to visualize 2D data such
as color or grayscale images, and 1D data such as contour lines, outlines
of segmented regions, histograms of gray levels, etc. Although
\texttt{matplotlib} has simple 3D plotting capabilities, we
recommend using the \texttt{mayavi} module \citep{Ramachandran2011}
for applications requiring advanced 3D visualization, such as tomography. 
\texttt{mayavi} is based on the VTK toolkit. It exposes a simple API for
visualizing data passed as \texttt{numpy} arrays. For example,
visualizing the surface of binary data can be written as
\begin{lstlisting}[language=Python]
# synthetic binary array from skimage.data
im = data.binary_blobs(length=400, n_dim=3).astype(np.uint8)
# visualization
from mayavi import mlab
mlab.contour3d(im)
mlab.outline()
\end{lstlisting}
(see Fig.~\ref{fig:mayavi} for the resulting visualization).

For more advanced visualizations, a large majority of VTK capabilities
can be accessed through mayavi's pipeline API. \texttt{mayavi} offers a
good trade-off between simplicity of use for common operations, and
accessibility to more sophisticated capabilities such as responsive
visualizations.

\begin{figure}[ht]
    \centerline{\includegraphics[width=0.6\columnwidth]{mayavi_example}}
    \caption{Simple visualization realized with Mayavi.
 \label{fig:mayavi}}
\end{figure}
